---
title: "Admin View"
output: html_document
---

```{r echo = FALSE}
library(magrittr)

base_url <- "https://dukefinance.wufoo.com/api/v3/"
username <- Sys.getenv("WUFOO_REGISTRATION_KEY")
password <- "footastic"

form_name <- "duke-fintech-trading-competition"

count_url       <- paste0(base_url, "forms/", form_name, "/entries/count.json")
registrants_url <- paste0(
  base_url, "forms/", form_name,
  "/entries.json?sort=EntryId&sortDirection=DESC&pageSize=100"
)

entries_count <- httr::GET(
  count_url, httr::authenticate(username, password)
) %>%
  httr::content() %>% {
    .$EntryCount
  } %>%
  as.numeric()

number_of_wufoo_queries <- ceiling(entries_count / 100)

registrants <- list()

for(i in 1:number_of_wufoo_queries){
  registrants <- c(
    registrants,
    httr::GET(
      paste0(registrants_url, "&pageStart=", i-1),
      httr::authenticate(username, password)
    ) %>%
      httr::content() %>% {
        .$Entries
      }
  )
}

registrants_df <- registrants %>%
  purrr::map(
    function(x){
      x %>%
        lapply(
          FUN = function(xx){
            if(is.null(xx)) return(NA)
            xx
          }
        ) %>%
        tibble::as_tibble()
    }
  ) %>%
  purrr::reduce(dplyr::bind_rows) %>%
  tidyr::unite(
    "work_situation",
    c("Field432", "Field433", "Field434"),
    sep = ""
  ) %>%
  dplyr::rename(
    "first_name"               = "Field1",
    "last_name"                = "Field2",
    "email"                    = "Field3",
    "expected_graduation_year" = "Field124",
    "university_wufoo"         = "Field4",
    "gradute_degree_program"   = "Field10",
    "undergrad_major"          = "Field120",
    "discord_name"             = "Field532",
    "trader_name"              = "Field5",
    "secret"                   = "Field130",
    "country_wufoo"            = "Field116",
    "gender"                   = "Field118",
    "website"                  = "Field126",
    "data_agreement"           = "Field534"
  ) %>%
  dplyr::mutate(
    "university" = university_wufoo %>% {
      dplyr::case_match(
        tolower(trimws(.)),
        c("duke", "duke university") ~ "Duke University",
        c(
          "johns hopkins", "johns hopkins university"
        ) ~ "Johns Hopkins University",
        c("ecu", "east carolina") ~ "East Carolina University",
        .default = trimws(.)
      )
    },
    "country" = country_wufoo %>% {
      dplyr::case_match(
        tolower(trimws(.)),
        c(
          "united state", "united states", "united stated", "usa", "us",
          "the unites states", "united states of america"
        ) ~ "USA",
        .default = trimws(.)
      )
    }
  )

```


# Everyone who has registered on WuFoo
As of date: "`r Sys.time()`"
``` {r echo = FALSE, message = FALSE}
DT::datatable(
  registrants_df,
  extensions = c('Scroller', 'Buttons'),
  rownames   = FALSE,
  options = list(
    columnDefs   = list(list(className = 'dt-center', targets = '_all')),
    dom         = 'Bt',
    buttons     = c('csv', 'excel', 'copy'),
    ordering    = FALSE,
    scrollY     = 500,
    scrollX     = '100%',
    scroller    = TRUE
  )
)
```

## Registration Stats:
```{r echo=FALSE}
print(paste0("Total registrants: ", entries_count))

print(
  paste0(
    "Universities: ", 
    paste0(unique(registrants_df$university), collapse = ", ")
  )
)
print("^^Check these for recoding")

print(table(registrants_df$university))

num_grad_students <- registrants_df$gradute_degree_program %>% {
  length(.[which(. != "")])
}

print(
  paste0(
    "Graduate Students: ", 
    num_grad_students, "; ", 
    signif(num_grad_students * 100 / entries_count, 3), "%"
  )
)

num_undergrad_students <- registrants_df$undergrad_major %>% {
  length(.[which(. != "")])
}

print(
  paste0(
    "Undergrad Students: ", 
    num_undergrad_students, "; ", 
    signif(num_undergrad_students * 100 / entries_count, 3), "%"
  )
)

print(table(registrants_df$country))

```

# IBKR Info
To make this part work, you need to clone the *fintech.trading.competition.private* 
repo to your computer. Do this in RStudio, same way we did for the public repo:
file > new project > version control > git, and then paste in the URL for the 
private repo, which you can get from your account in the GitHub website.

That repo contains a private file with everyone's name, email, and IBKR account
number. We can use this to match up account numbers with actual traders. 

We can also use it to track who has registered on WooFoo but hasn't set up an 
account yet!

## Registered & accounts set up:
```{r, echo=FALSE}
if(file.exists("../fintech.trading.competition.private/whois.xml")){
  ibkr_account_info <- "../fintech.trading.competition.private/whois.xml" %>%
    readLines() %>% 
    paste0(collapse="") %>%
    xml2::read_xml() %>%
    xml2::xml_child("FlexStatements") %>% 
    xml2::as_list() %>%
    lapply(
      FUN = function(x){
        tibble::tibble(
          "name" = attr(x$AccountInformation, "name"),
          "account_id" = attr(x$AccountInformation, "accountId"),
          "email" = attr(x$AccountInformation, "primaryEmail")
        )
      }
    ) %>%
    purrr::reduce(dplyr::bind_rows)
  
  registrants_df %>%
    dplyr::inner_join(
      ibkr_account_info, 
      by = "email"
    ) %>% 
    dplyr::select(
      name, first_name, last_name, account_id, email, discord_name, trader_name
    ) %>%
    DT::datatable(
      registrants_df,
      extensions = c('Scroller', 'Buttons'),
      rownames   = FALSE,
      options = list(
        columnDefs   = list(list(className = 'dt-center', targets = '_all')),
        dom         = 'Bt',
        buttons     = c('csv', 'excel', 'copy'),
        ordering    = FALSE,
        scrollY     = 500,
        scrollX     = '100%',
        scroller    = TRUE
      )
    )
} else {
  print("fintech.trading.competition.private is not found")
}
```

## Emails that still need an IBKR invite:
```{r echo=FALSE}
if(file.exists("../fintech.trading.competition.private/whois.xml")){
  setdiff(registrants_df$email, ibkr_account_info$email) %>%
    paste0(collapse = ",")
} else {
  print("fintech.trading.competition.private is not found")
}
```
