---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
refresh_all_data()
most_recent_date <- participating_student_reports$total %>%
  lapply(
    function(ttl){
      as.character(as.Date(zoo::index(xts::last(ttl))))
    }
  ) %>%
  unlist(use.names = FALSE) %>%
  unique() %>%
  as.Date()
if(length(most_recent_date) != 1){
  print(most_recent_date)
  stop("more than one most recent date found!")
}
earliest_date <- participating_student_reports$total %>%
  lapply(
    function(ttl){
      as.character(as.Date(zoo::index(xts::first(ttl))))
    }
  ) %>%
  unlist(use.names = FALSE) %>%
  unique() %>%
  as.Date()
if(length(most_recent_date) != 1){
  print(most_recent_date)
  stop("more than one earliest date found!")
}
```

# Duke FINTECH Trading Competition 2021
The Duke FINTECH Trading Competition is a free competition open to any currently enrolled graduate or undergraduate student with a .edu address.

Participants are granted paper trading accounts at [Interactive
Brokers](https://www.interactivebrokers.com/en/index.php?f=1338&gclid=CjwKCAjw6fCCBhBNEiwAem5SO84OkMDwq8mlx6lCjOmAmCNDUaLbhxtQuFSUlozy6iLEZtmsve2w-hoCQ9sQAvD_BwE),
which enable them to trade equities, options, ETFs, futures, currencies, bonds,
and more, all based on real-time streaming market data. Students use the same
execution systems as professional traders: (IBKR's [Mobile
App](https://www.interactivebrokers.com/en/index.php?f=1300), [Trader
Workstation GUI](https://www.interactivebrokers.com/en/index.php?f=16040) and
[IB Gateway](https://www.interactivebrokers.com/en/index.php?f=16457)) -- the
only difference is that the money they trade is simulated.

The Spring 2021 session is currently underway. We are pleased that about 90
students at various universities have signed up for this session, which is the
very first offering of the competition outside of Duke.

The Duke FINTECH Department is striving to be as inclusive and welcoming as
possible to all students, and will be reaching out again next Fall for the next
offering. Participation is welcome and encouraged, so please help spread the
word for future semesters!

Standings for the top 10 traders will be posted here and updated daily. This
site will continue to grow as new features are brought onboard. Be sure to
check back often for updates!!!

## Standings as of `r Sys.Date()`
Updated for the available data range from `r earliest_date` to `r most_recent_date`.

``` {r echo = FALSE, message = FALSE}
participating_student_reports %>%
  head(10) %>%
  dplyr::mutate(
    "Ranking"             = 1:10,
    "Trader"              = trader_name,
    "Daily Excess Return" = paste0(round(excess_gmrr, 5), "%"),
    "Daily Vol"           = paste0(round(daily_vol, 5), "%"),
    "Sharpe Ratio"        = round(Sharpe, 3)
  ) %>%
  dplyr::select(
    Ranking, Trader, School, `Daily Excess Return`, `Daily Vol`, `Sharpe Ratio`
  ) %>%
  kableExtra::kable(
    caption = paste0("Top 10 Sharpe Ratios as of ", Sys.Date()), 
    escape  = FALSE,
    align   = rep('c', 5)
  )
```
