---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Welcome to the 2021 Duke FINTECH Trading Competition

This is the homepage of the Competition, and is the location where rankings will
be updated. will be posted. Be sure to check the "NEWS" section for
announcements, and the "Articles" section for important information such as
scoring of results.

<!-- badges: start -->
<!-- badges: end -->

## --> ToDo: Check your account number

First things first: This year (Spring 2021), a few participants have created
multiple accounts, and others have created accounts using emails that differ
from the ones used in the WuFoo sign-up sheet. In the future, functionality will
be written into the onboarding process to avoid this, but for now, I (Jake) have
manually matched each participant's account number & username.

It's up to you to check and make sure that the account you'd like to use for the
competition is the one that appears next to your username.

**Please check the chart below and make sure that the account number appearing
next to your name is the one that you want to use for the competition**.

If I've got the wrong account number listed for you, please let me (Jake) know
on the Slack channel.


``` {r echo = FALSE, message = FALSE}
rprojroot::find_package_root_file() %>%
  file.path("inst", "participants", "joined_names_n_emails.csv") %>%
  readr::read_csv() %>%
  dplyr::filter(!is.na(ID)) %>%
  dplyr::select(accountId, trader_name) %>%
  dplyr::arrange(trader_name) %>%
  kableExtra::kable(caption = "Trader IDs and Account Numbers", escape = FALSE)
```
