---
title: "Update 19 Feb 2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Update 19 Feb 2022}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r, echo = FALSE}
shiny::tagList(
  shiny::fluidRow(
    shiny::fluidRow(
      shiny::column(width = 6, shiny::p("19 Feb 2022", class = "article-date"))
      # ,
      # shiny::column(
      #   width = 6,
      #   shiny::p(
      #     shiny::a(
      #       "Link to Official Announcement",
      #       href="https://fintech.meng.duke.edu/news/duke-fintech-intercollegiate-trading-competition-kicks-spring-2022"
      #     ),
      #     class = "original-article-link"
      #   ),
      # )
    ),
    shiny::p(
      "Duke FinTech Annual InterCollegiate\n\nTrading Competition",
      class = "announcement-title"
    )
  ),
  shiny::fluidRow(
    shiny::p("Sponsored by:"),
    class = "sponsored-by"
  ),
  shiny::fluidRow(
    style = "display: flex; align-items: center; justify-content: center;",
    shiny::column(
      width = 4, 
      shiny::a(shiny::img(src = "finvc_logo.png"), href = "https://finvc.co/")
    ),
    shiny::column(
      width = 4, 
      shiny::a(shiny::img(src = "horizen_logo.png"), href = "https://www.horizen.io/")
    ),
    shiny::column(
      width = 4,
      shiny::a(shiny::img(src = "mesh_logo.png"), href = "https://mesh.xyz/")
    )
  ),
  shiny::fluidRow(
    shiny::p(
      paste0(
        "There’s been an upset! The two frontrunners – Hoppity and Bubbles – have been battling it out for first place by running strategies that generate small but reliable daily returns with almost zero volatility. On 17 Feb, Bubble’s strategy took a downturn, placing him in 3rd place with a Sharpe ratio of 0.44, just behind Trader Raven, who now occupies 2nd place with a Sharpe of 0.56."  
      ),
      class = "subtitle"
    )
  )
)
```

<p class = "basic-text"> Hoppity remains in the lead with a commanding Sharpe of
ratio of 16.78. Bubbles, Hoppity and Trader Raven were asked to provide a few
words about themselves and their strategies. Trader Raven could not be reached
for comment.</p>

<p class = "basic-text">Bubbles had this to say:</p>
*My name is Tanner Hoke and I am a Computer Science major at Texas A&M
University. I noticed that the trading competition is scored based on Sharpe
ratio, and thought that if I could find a strategy to make the denominator
(which is EoD volatility) close to zero, I might have a shot at winning. I won’t
go into too much detail about my strategy, but it involves a high probability of
generating a consistent and small positive return every day. It’s possible that
it fails somewhat catastrophically, though; we will see!*

<p class = "basic-text">Hoppity provided the following:</p>
*I am Richard, a senior at Harvard University studying Math and Statistics. I had
some previous experience with quantitative trading, and will be working at a
proprietary trading firm next year. I'm super excited for the competition since
the scoring function is more interesting than traditional trading competitions!
Since the goal of the competition is to maximize the Sharpe ratio, it is crucial
to reduce my risk and variance as much as possible. I am running an automated
trading strategy that aims to make a constant and positive returns every day.
The automated strategy allows me to avoid most market risks that are unavoidable
with "buy and hold" strategies, thus maximizing my Sharpe. I hope to keep this
up for the rest of the competition. Computer code is prone to errors, and it
seems like another competitor is right on my tail!*

<p class = "basic-text">Will Bubbles recover and overtake the frontrunners for
first place? Will Hoppity’s strategy continue as expected and keep him in the
lead? Will Trader Raven continue to rake in cash while maintaining a very
respectable Sharpe?</p>

<p class = "basic-text">Check back to see how this competition plays out! This
site is updated daily.</p>


```{css, echo = FALSE}
h1, .dont-show {
display: none;
}

.announcement-title {
text-align: center;
font-size: 54px;
margin-top: 30px;
color: #FFD960;
}

.basic-text{
padding-top:10px;
padding-bottom:10px;
}

.basic-link, .basic-text, .quote{
font-size:18px;
}

.school-name{
color: Cornsilk;
font-size:19px;
}

.subtitle{
color:#bdd9d9;
font-size:25px;
font-style:italic;
text-align:center;
}

.sponsored-by{
font-size:25px;
font-style:bold;
text-align:center;
}

.article-date{
padding-top:10px;
text-align:left;
font-weight:bold;
color:#FCF7E5;
}

.original-article-link{
padding-top:10px;
text-align:right;
}

.quote {
color:#FCF7E5;
}

.table-header {
color:#FFD960;
font-size:22px;
}

```

