---
title: "Calculating Excess Return, Volatility & Sharpe"
output: html_document
---

```{css, echo=FALSE}
.dt-colnames {
color: #fcba03;
}
.dataTables_paginate, tbody {
background-color: white;
}
```

```{r setup, include = FALSE}
library(magrittr)
format_percent <- function(number, suffix){
  paste0(signif(number*100, 4), suffix)
}
```

```{r echo=FALSE}
shiny::fluidRow(
  shiny::column(2),
  shiny::column(
    8,
    vembedr::embed_url("https://youtu.be/2sPWmHHgZNA")
  ),
  shiny::column(2)
)
```

At the end of every trading day -- as soon as a new end-of-day Net Account Value (NAV) for all the traders in the competition becomes available (usually around 7pm EST) -- the following process is run to calculate the **Excess Return** and **Volatility** for every participant.

  - **Excess Return** ($R_{p} - r_{f}$) is the difference between the return your portfolio earned ($R_{p}$) and the risk free rate ($r_{f}$)
  - **volatility** of returns ($\sigma_{p}$) is defined as the standard deviation of your portfolio's daily log returns.

In this section we'll demonstrate how we calculate these numbers using some
made-up example data for a hypothetical trader.

## Example Trader's Data
Let's say that today's date is 23 March 2021, and a student has been
participating in the competition for seven days. 

Her end-of-day (EoD) Net Asset Value (NAV) and daily log returns are:

``` {r echo = FALSE, message = FALSE}
student_data <- tibble::tibble(
  "Date"     = c(
    "2021-03-23", "2021-03-22", "2021-03-19", "2021-03-18", "2021-03-17", 
    "2021-03-16", "2021-03-15"
  ),
  "EoD NAV"  = c(
    1000301, 1000075, 1000250, 1000050, 1000100, 999890,  999950
  ),
  "Port. Return (%/trd day)" = c(
    log(`EoD NAV`[-length(`EoD NAV`)] / `EoD NAV`[-1] ),
    NA
  )
)
student_data %>%
  DT::datatable(
    rownames = FALSE,
    options  = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      ordering    = FALSE
    )
  ) %>%
  DT::formatCurrency(columns = "EoD NAV") %>%
  DT::formatPercentage("Port. Return (%/trd day)", digits = 5)
```

Note that there's no way to calculate a return on the very first day because
there's nothing to compare it to.

The student's **daily portfolio returns** are the log returns of her daily
portfolio value. For example, on 18 March 2021, she started the day with
\$1,000,100.00 and ended with \$1,000,050.00 in total portfolio value. Therefore
the return she sees at end-of-day on 18 March 2021 was:
```{r}
# 'log()' here is the natural log, not base 10.
rtn_18_mar_2021 <- log(1000050.00 / 1000100.00)
format_percent(rtn_18_mar_2021, "% / trading day.")
```

Let's check that, because why not? She started the day with $1,000,100.00 NAV, 
so that number * (1 + $return$) should equal the $1,000,050.00 NAV that her 
account posted at day's end:
```{r}
# check
1000100.00 * (1 + rtn_18_mar_2021)
```
--> Looks good.

The student's overall **geometric mean rate of return** $R_{p}$ for the entire 
time period is:
```{r}
student_gmrr <- student_data %>%
  dplyr::select("Port. Return (%/trd day)") %>%
  dplyr::filter(!is.na(`Port. Return (%/trd day)`)) %>% 
  tibble::deframe() %>% {
    prod(1 + .)^(1/length(.)) - 1
  }
format_percent(student_gmrr, "% / trading day.")
```


## What risk-free rate do we use?
The Gothic Hedge Society (who runs the trading competition) reasons that on Day
1, all participants implicitly decide if they're going to actively trade at all,
as opposed to simply putting all of their money into risk-free debt with a 
maturity near the Competition's end date.

Sounds like not a lot of fun and not a good way to make a fortune... but since 
about half of the participants will *lose* money in this contest, the idea isn't
actually as bad as it might sound.

Regardless, for the duration of the Competition, the value of $r_{f}$ used to 
calculate Sharpes does not change, even though new risk-free rates will be 
published every day by the USDT. The reason why we keep $r_{f}$ fixed is because
we're comparing your performance as a trader to the "base strategy": simply
buying debt earning $r_{f}$ on Day 1, which would tie up all your capital for 
trading until maturity on the last day.

Since the Competition lasts about **3 months**, the value we'll use for $r_{f}$ 
will be whatever the USDT publishes as the 3-month CMT rate on the day the 
Competition starts. This value will be will be posted clearly and conspicuously
for everyone.

**For this example**, let's suppose that on Day 1 we visited the USDT's website 
and found that the 3-month CMT rate was 0.04% (annualized). 

We want that on a trading day basis, so we'll convert: since there are 252 
trading days in a year, we divide by 252 (and by 100 because it's a percent):

Let's do that now, and store $r_{f}$ as a variable:
``` {r echo = FALSE, message = FALSE}
rf = 0.04/100/252
print(paste0("The risk-free rate is ", format_percent(rf, "% / trading day.")))
```

## Excess Return
Now that we have values for $R_{p}$ and $r_{f}$ student's **excess return** is
```{r}
student_excess_return <- student_gmrr - rf
format_percent(student_excess_return, "% / trading day.")
```

## Volatility
The students **volatility of returns** $\sigma_{p}$ is the standard 
deviation of her portfolio returns:
```{r}
student_vol <- student_data %>%
  dplyr::select("Port. Return (%/trd day)") %>%
  dplyr::filter(!is.na(`Port. Return (%/trd day)`)) %>% 
  tibble::deframe() %>%
  sd()
format_percent(student_vol, "% / trading day.")
```

## Sharpe ratio
We now have everything we need to calculate this trader's Sharpe ratio:

\begin{align*}
{\tt Sharpe\ Ratio} = \frac{R_{p} - r_{f}}{\sigma_{p}} 
\end{align*}

#### Wherein:

\begin{align*}
R_{p} & {\sf: Portfolio\ Return} \\
r_{f} & {\sf: Risk\ free\ rate\ of\ return} \\
\sigma_{p} & {\sf: Volatility\ of\ portfolio\ return}
\end{align*}

## Her Sharpe is therefore:
```{r}
student_Sharpe <- (student_gmrr - rf) / student_vol
print(student_Sharpe)
```


#### Matching up Calculations w/ Excel and Other Programs (a quick note)
As simple as it may seem, calculating logarithms can differ slightly (or
sometimes, significantly) depending on the precision of the program you use.
It's possible to get different answers for the same log calcs in Excel, R, and
Python, and the difference gets magnified when calculating GMRR.

Therefore, don't worry too much if you try to follow along this example and wind
up with numbers that differ slightly. For the purposes of fairness in the
competition, it only matters that we use the same program for everyone -- which,
in this case, is the *log*() function in R.

