---
title: "Incentive Structure - Discussion"
output: html_document
---

```{r setup, include = FALSE}
library(magrittr)
```

```{r echo=FALSE}
shiny::fluidRow(
  shiny::column(2),
  shiny::column(
    8,
    vembedr::embed_url("https://youtu.be/3Vyco-nhsk0")
  ),
  shiny::column(2)
)
```

In the [Ranking](https://gothic-hedge-society.github.io/fintech.trading.competition/articles/ranking.html) section we described our scoring system which bins traders 
into **brackets** according to their average returns, then sorts them within
brackets according to their Sharpe ratios.

The Gothic Hedge Society prefers this structure because it's consistent with our
values of rewarding intelligent risk-taking, but it also comes with several 
other desirable qualities:

#1. It makes the Competition interesting to watch
You can't win cash prizes unless you're in the top half of the top bracket -- 
which you can only accomplish if you post a big return. **BUT**, within that 
bracket you're placed towards the bottom if you have a high volatility, meaning
that you won't win any real money.

This is the reason why we chose $n$ = 10 for the bracket sizes -- that's 2x the
number of paid cash slots available. 

Those traders who are **not** in the top bracket are incentivized to get there
by making more money. 

Those who **are** in the top bracket are incentivized to watch their volatility 
so that they can stay there, or increase their rank. **But**... decreasing 
volatility means that those top traders will probably have to sacrifice in terms
of returns... which risks them being bumped into a lower bracket!

#2. It keeps traders interested throughout the entire event
If you're in a lower bracket and don't have much hope of reaching a top slot 
before the Competition ends, you are **still** interested in trading because 
you want to reach the top of your bracket -- and maybe reach the next one up. It
gives everyone a shot at winning some bragging rights ("I was #3 in my bracket")
and telling a good story to potential interviewers about how you handled a rough
situation and improved it as much as possible. 

Jake & Zoe are open to the idea of awarding cash prizes to lower brackets; also
in awarding "side prizes" for impressive feats such as high returns, low beta, 
and so on. This, of course, depends upon interest and capital availability.

#3. It prevents 'Sharpe Ratio Hacking'
Last year the competition was scored using Sharpe ratio alone, but two very 
disciplined traders -- Hoppity and Bubbles -- dominated the competition by 
running a strategy that earned a tiny return with a volatility that was even
smaller, resulting in **massive** Sharpe ratios. The Gothic Hedge Society found
this behavior to be:

  - innovative
  - fair
  - extremely annoying :)
  
We salute Hoppity and Bubbles -- who are great people -- for their success but 
we want to be sure that others don't follow suit because at the end of the day 
this competition is about making money.
