---
title: "Determining Trader Ranks"
output: html_document
---

```{r setup, include=FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(echo = TRUE)
```

If you've made it to this page, you're looking to understand how we assign 
rankings to each trader to determine a winner. In order to proceed, you should
have already read and understood the [General Idea behind our scoring philosophy]([Scoring](https://gothic-hedge-society.github.io/fintech.trading.competition/articles/Scoring.html))
to get an idea of what we're seeking to do; to wit: reward those traders who 
make a lot of money, but do so intelligently rather than just getting lucky.


The process described below is performed daily when standings are updated.

## Step 1: START
For every trader in the Contest, we calculate geometric mean excess return and 
Sharpe ratio as described in [Sharpe Ratio Calculation](https://gothic-hedge-society.github.io/fintech.trading.competition/articles/Sharpe Ratio Calculation.html).

Let's suppose that we have 50 traders in the competition and on this particular
day they come out with the following stats:
``` {r echo = FALSE, message = FALSE}
DT::datatable(
    example_standings,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatPercentage(2, digits = 5) %>%
  DT::formatSignif(3, 5)
```

## Step 1: Sort by excess return
We arrange everyone by excess return. Highest return goes at the top and the 
lowest goes to the bottom, leaving us with:
``` {r echo = FALSE, message = FALSE}
DT::datatable(
    dplyr::arrange(example_standings, dplyr::desc(`excess return`)),
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatPercentage(2, digits = 5) %>%
  DT::formatSignif(3, 5)
```

## Step 2: Break the traders down into brackets of 10
Prizes are awarded to the top 5 traders, so we form brackets of 10 traders each
(=5*2) based on excess return. That leaves us with the below, where each page
of the datatable is a single bracket:
``` {r echo = FALSE, message = FALSE}
example_standings_step2 <- example_standings %>%
  dplyr::arrange(dplyr::desc(`excess return`)) %>% {
    n <- 10
    n_brackets  <- nrow(.) %/% n
    remainder <- nrow(.) %% n
    bracket <- rep(n_brackets, n + remainder)
    for (i in (n_brackets-1):1){
      bracket <- c(rep(i, n), bracket)
    }
    .$bracket <- bracket
    .
  } %>%
  dplyr::select(bracket, dplyr::everything()) 

DT::datatable(
    example_standings_step2,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      pageLength = 10,
      dom         = 'Btp',
      buttons     = c('csv', 'excel', 'copy')
    )
  ) %>%
  DT::formatPercentage(3, digits = 5) %>%
  DT::formatSignif(4, 5)
```

### Step 3: Sort by Sharpe within brackets
Each individual group of 10 traders is sorted with highest Sharpe at the top,
lowest at the bottom.
``` {r echo = FALSE, message = FALSE}
example_standings_step3 <- example_standings %>%
  dplyr::arrange(dplyr::desc(`excess return`)) %>% {
    n <- 10
    n_brackets  <- nrow(.) %/% n
    remainder <- nrow(.) %% n
    bracket <- rep(n_brackets, n + remainder)
    for (i in (n_brackets-1):1){
      bracket <- c(rep(i, n), bracket)
    }
    .$bracket <- bracket
    .
  } %>%
  dplyr::select(bracket, dplyr::everything()) %>%
  dplyr::group_by(bracket) %>%
  dplyr::arrange(dplyr::desc(Sharpe), .by_group = TRUE) 

DT::datatable(
    example_standings_step3,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      pageLength = 10,
      dom         = 'Btp',
      buttons     = c('csv', 'excel', 'copy')
    )
  ) %>%
  DT::formatPercentage(3, digits = 5) %>%
  DT::formatSignif(4, 5)
```

## Step 4: Assign bracket ranks
Everyone is given a rank within their bracket:
``` {r echo = FALSE, message = FALSE}
example_standings_step4 <- example_standings_step3 %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    "bracket rank" = paste0(bracket, "-", rep(1:10, 5))
  ) %>%
  dplyr::select(`bracket rank`, dplyr::everything()) %>%
  dplyr::select(-bracket)

DT::datatable(
    example_standings_step4,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      pageLength = 10,
      dom         = 'Btp',
      buttons     = c('csv', 'excel', 'copy')
    )
  ) %>%
  DT::formatPercentage(3, digits = 5) %>%
  DT::formatSignif(4, 5)
```

## Step 5: Recombine into one table and assign overall trader rank
This determines overall rank for the competition:
``` {r echo = FALSE, message = FALSE}
example_standings_final <- example_standings_step4 %>%
  dplyr::mutate(
    "rank" = 1:nrow(.)
  ) %>%
  dplyr::select(rank, dplyr::everything())

DT::datatable(
    example_standings_final,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatPercentage(4, digits = 5) %>%
  DT::formatSignif(5, 5)
```
