---
title: "Fully Worked Scoring & Ranking Example"
output: html_document
---

```{css, echo=FALSE}
button.dt-button {
font-size: 14px;
color: greenyellow;
border: 1px solid white;
}
.key-heading {
font-size: 20px;
font-weight: bold;
}
.dataTables_paginate, tbody {
background-color: white;
}
```

```{r setup, include=FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
shiny::fluidRow(
  shiny::column(2),
  shiny::column(
    8,
    vembedr::embed_url("https://youtu.be/2sPWmHHgZNA")
  ),
  shiny::column(2)
)
```

If you've made it to this page, you're looking to understand how we assign 
rankings to each trader to determine a winner. In order to proceed, you should
have already read and understood the [General Idea behind our scoring philosophy](https://gothic-hedge-society.github.io/fintech.trading.competition/articles/Scoring.html)
to get an idea of what we're seeking to do; to wit: reward those traders who 
make a lot of money, but do so intelligently rather than just getting lucky.

The process described below is performed daily when standings are updated.

## Step 1: START
For every participaiting trader, every day as soon as new end-of-day NAV values
become available, we calculate excess return and Sharpe ratio as described in 
[Sharpe Ratio Calculation](https://gothic-hedge-society.github.io/fintech.trading.competition/articles/Sharpe Ratio Calculation.html).

Let's suppose that we have 50 traders in the competition and on this particular
day we run the query, do the calculations, and end up with the following stats:
``` {r echo = FALSE, message = FALSE}
DT::datatable(
  example_standings,
  extensions = c('Scroller', 'Buttons'),
  rownames   = FALSE,
  options = list(
    columnDefs   = list(list(className = 'dt-center', targets = '_all')),
    initComplete = DT::JS(
      "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
    ),
    dom         = 'Bt',
    buttons     = c('csv', 'excel', 'copy'),
    ordering    = FALSE,
    scrollY     = 500,
    scrollX     = '100%',
    scroller    = TRUE
  )
) %>%
  DT::formatPercentage(2, digits = 5) %>%
  DT::formatSignif(3, 5)
```

## Step 1: Sort by excess return
The first thing we do is arrange everyone in the table by decreasing excess 
return. Highest return goes at the top and the lowest goes to the bottom, 
leaving us with:
``` {r echo = FALSE, message = FALSE}
DT::datatable(
  dplyr::arrange(example_standings, dplyr::desc(`excess return`)),
  extensions = c('Scroller', 'Buttons'),
  rownames   = FALSE,
  options = list(
    columnDefs   = list(list(className = 'dt-center', targets = '_all')),
    initComplete = DT::JS(
      "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
    ),
    dom         = 'Bt',
    buttons     = c('csv', 'excel', 'copy'),
    ordering    = FALSE,
    scrollY     = 500,
    scrollX     = '100%',
    scroller    = TRUE
  )
) %>%
  DT::formatPercentage(2, digits = 5) %>%
  DT::formatSignif(3, 5)
```

## Step 2: Break the traders down into brackets of 10
Prizes are awarded to the top 5 traders, so we form brackets of 10 traders each
(=5*2) based on excess return. That leaves us with the below, where each page
of the datatable is a single bracket:
``` {r echo = FALSE, message = FALSE}
example_standings_step2 <- example_standings %>%
  dplyr::arrange(dplyr::desc(`excess return`)) %>% {
    n <- 10
    n_brackets  <- nrow(.) %/% n
    remainder <- nrow(.) %% n
    bracket <- rep(n_brackets, n + remainder)
    for (i in (n_brackets-1):1){
      bracket <- c(rep(i, n), bracket)
    }
    .$bracket <- bracket
    .
  } %>%
  dplyr::select(bracket, dplyr::everything()) 

DT::datatable(
  example_standings_step2,
  extensions = 'Buttons',
  rownames   = FALSE,
  options = list(
    columnDefs   = list(list(className = 'dt-center', targets = '_all')),
    initComplete = DT::JS(
      "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
    ),
    pageLength = 10,
    ordering    = FALSE,
    dom         = 'Btp',
    buttons     = c('csv', 'excel', 'copy')
  )
) %>%
  DT::formatPercentage(3, digits = 5) %>%
  DT::formatSignif(4, 5)

```

### Step 3: Sort by Sharpe within brackets
Each individual group of 10 traders is sorted with highest Sharpe at the top,
lowest at the bottom.
``` {r echo = FALSE, message = FALSE}
example_standings_step3 <- example_standings %>%
  dplyr::arrange(dplyr::desc(`excess return`)) %>% {
    n <- 10
    n_brackets  <- nrow(.) %/% n
    remainder <- nrow(.) %% n
    bracket <- rep(n_brackets, n + remainder)
    for (i in (n_brackets-1):1){
      bracket <- c(rep(i, n), bracket)
    }
    .$bracket <- bracket
    .
  } %>%
  dplyr::select(bracket, dplyr::everything()) %>%
  dplyr::group_by(bracket) %>%
  dplyr::arrange(dplyr::desc(Sharpe), .by_group = TRUE) 

DT::datatable(
  example_standings_step3,
  extensions = c('Scroller', 'Buttons'),
  rownames   = FALSE,
  options = list(
    columnDefs   = list(list(className = 'dt-center', targets = '_all')),
    initComplete = DT::JS(
      "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
    ),
    pageLength = 10,
    ordering    = FALSE,
    dom         = 'Btp',
    buttons     = c('csv', 'excel', 'copy')
  )
) %>%
  DT::formatPercentage(3, digits = 5) %>%
  DT::formatSignif(4, 5)
```

## Step 4: Assign bracket ranks
Everyone is given a rank within their bracket:
``` {r echo = FALSE, message = FALSE}
example_standings_step4 <- example_standings_step3 %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    "bracket rank" = paste0(bracket, "-", rep(1:10, 5))
  ) %>%
  dplyr::select(`bracket rank`, dplyr::everything()) %>%
  dplyr::select(-bracket)

DT::datatable(
  example_standings_step4,
  extensions = c('Scroller', 'Buttons'),
  rownames   = FALSE,
  options = list(
    columnDefs   = list(list(className = 'dt-center', targets = '_all')),
    initComplete = DT::JS(
      "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
    ),
    pageLength = 10,
    ordering    = FALSE,
    dom         = 'Btp',
    buttons     = c('csv', 'excel', 'copy')
  )
) %>%
  DT::formatPercentage(3, digits = 5) %>%
  DT::formatSignif(4, 5)
```

## Step 5: Recombine into one table and assign overall trader rank
This determines overall rank for the competition:
``` {r echo = FALSE, message = FALSE}
example_standings_final <- example_standings_step4 %>%
  dplyr::mutate(
    "rank" = 1:nrow(.)
  ) %>%
  dplyr::select(rank, dplyr::everything())

DT::datatable(
  example_standings_final,
  extensions = c('Scroller', 'Buttons'),
  rownames   = FALSE,
  options = list(
    columnDefs   = list(list(className = 'dt-center', targets = '_all')),
    initComplete = DT::JS(
      "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
    ),
    dom         = 'Bt',
    buttons     = c('csv', 'excel', 'copy'),
    deferRender = TRUE,
    ordering    = FALSE,
    scrollY     = 500,
    scrollX     = '100%',
    scroller    = TRUE
  )
) %>%
  DT::formatPercentage(4, digits = 5) %>%
  DT::formatSignif(5, 5)
```

## Conclusion
Traders 18, 16, 11, 36, and 10 take the top 5 spots in the competition overall.
