---
title: "Reference Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reference Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE, echo=FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here is the reference data used in the scoring. Feel free to use the buttons to
download this info for your own analysis!


```{css, echo=FALSE}
button.dt-button {
font-size: 14px;
color: greenyellow;
border: 1px solid white;
}
.key-heading {
font-size: 20px;
font-weight: bold;
}
```

# Market Data
Used for calculating daily risk-free rates for excess returns and for
calculating beta with respect to three market benchmarks: SP500, SHY, and BTC.
These benchmarks were chosen because:

* The **SP500** is probably the most most commonly used market benchmark in
finance and financial reporting

* We wanted to include a benchmark that had virtually NO correlation with the
**SP500** so we selected **SHY**

* **BTC-USD** is interesting and timely, so it's interesting to include. 

<p class='key-heading'>Key:</p>

```{r, echo=FALSE}
data.frame(
  "Column_Name" = c(
    "Date", "SP500", "SP500_rtn", "SHY", "SHY_rtn", "BTC-USD", "BTC-USD", 
    "3_mo", "3_mo_apy", "3_mo_td"
  ),
  "Description" = c(
    "Date on which the value in a column was observed",
    "Closing value of the S&P 500 index", 
    "Daily return of the S&P 500 index",
    "Closing value of the iShares 1-3 year treasury bond ETF",
    "Daily return of the iShares 1-3 year treasury bond ETF",
    "Closing value of Bitcoin/USD exchange rate",
    "Daily return of the Bitcoin/USD exchange rate",
    "Daily 3-month maturity treasury par yield curve rate [as reported by the US Department of the Treasury](https://home.treasury.gov/resource-center/data-chart-center/interest-rates/TextView?type=daily_treasury_yield_curve&field_tdr_date_value_month=202202)",
    "US Treasury 3-month yields converted to Annual Percentage Yield (APY) using the [USDT's formula](https://home.treasury.gov/policy-issues/financing-the-government/interest-rate-statistics/interest-rates-frequently-asked-questions)",
    "3-month APY expressed on a per-trading-day basis by dividing by 252"
  )
) %>%
  kableExtra::kbl(col.names = NULL) %>%
  kableExtra::column_spec(
    column       = 1, 
    bold         = TRUE, 
    border_right = "2px solid #FFD960", 
    color        = "greenyellow"
  ) %>%
  kableExtra::kable_styling(bootstrap_options = "condensed")
```

**Why BTC-USD is interesting**: If you wind up with a large beta (positive or
negative) with respect to **BTC-USD**, then that means that whatever trading
strategy you're running is "accidentally(?)" [closet
indexing](https://www.investopedia.com/terms/c/closetindexing.asp#:~:text=Closet%20indexing%20is%20a%20strategy,without%20exactly%20replicating%20the%20index.)
Bitcoin. Usually closet indexing is a bad thing, but consider: Certainly you
based your trading strategy on valid assumptions about the market. If your
strategy turns out to have a strong beta with respect to **BTC-USD**, then that
means that whatever market principles are at work in your strategy are also at
work in Bitcoin price discovery. *That* means that just maybe, with some
insight, you can take a deep look at your strategy and do something that many
consider almost impossible: model the price behavior of Bitcoin reliably!

```{r echo=FALSE}
ref_data %>%
  dplyr::mutate(
    '3_mo'     = .$`3_mo`/100,
    '3_mo_apy' = .$`3_mo_apy`/100,
    '3_mo_td'  = .$`3_mo_td`/100,
  ) %>%
  DT::datatable(
    .,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatPercentage(
    columns = c(
      'SP500_rtn', 'SHY_rtn', 'BTC-USD_rtn',  '3_mo', '3_mo_apy', '3_mo_td'
    ), 
    digits = c(3, 3, 3, 3, 3, 5)
  )
```


# Portfolio Values
End-of-day value of each trader's portfolio.
```{r echo=FALSE}
eod_account_value %>%
  DT::datatable(
    .,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatCurrency(colnames(eod_account_value)[-1])
```

# Portfolio Returns
Daily log returns for each trader

```{r echo=FALSE}
eod_returns %>%
  DT::datatable(
    .,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatPercentage(colnames(eod_returns)[-1], 5)
```

# EoD Excess Return
Daily return the minus risk-free rate (3_mo_td) for that day.

```{r echo=FALSE}
eod_excess_returns %>%
  DT::datatable(
    .,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatPercentage(colnames(eod_excess_returns)[-1], 5)
```

# Cumulative Excess Return
Calculated as gmrr of excess returns observed up to the given date.

One unique complication: when a trader has an odd number of very negative daily
returns, the arithmetic mean rate of return is used because the geometric mean
can't be calculated -- you can't take a real-valued root of a negative number.

```{r echo=FALSE}
cumulative_eod_excess_returns %>%
  DT::datatable(
    .,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatPercentage(colnames(cumulative_eod_excess_returns)[-1], 5)
```

# Cumulative Volatility
Standard deviation of portfolio returns (not excess) up to each date.

```{r echo=FALSE}
cumulative_vol %>%
  DT::datatable(
    .,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatPercentage(colnames(cumulative_vol)[-1], 5)
```

# Sharpe
Cumulative excess return / cumulative portfolio volatility

```{r echo=FALSE}
sharpes %>%
  DT::datatable(
    .,
    extensions = c('Scroller', 'Buttons'),
    rownames   = FALSE,
    options = list(
      columnDefs   = list(list(className = 'dt-center', targets = '_all')),
      initComplete = DT::JS(
        "
      function(settings, json) {
          $(this.api().table().header()).css({
              'color' : 'greenyellow'
          });
      }
      "
      ),
      dom         = 'Bt',
      buttons     = c('csv', 'excel', 'copy'),
      deferRender = TRUE,
      ordering    = FALSE,
      scrollY     = 500,
      scrollX     = '100%',
      scroller    = TRUE
    )
  ) %>%
  DT::formatSignif(colnames(sharpes)[-1], 5)
```
