---
title: "Registry"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Registry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include=FALSE, echo=FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
.dataTables_filter label {
font-size: 18px;
color: greenyellow;
}
```

```{r, echo=FALSE}
Sys.time() %>%
  lubridate::with_tz(tzone = 'EST') %>% {
    
    two_digit_pad <- function(number){
      number <- floor(as.numeric(number))
      if(floor(number) < 10) return(paste0("0", number))
      as.character(number)
    }    
    
    paste0(
      two_digit_pad(lubridate::day(.)),    " ", 
      lubridate::month(., label = TRUE),   " ",
      lubridate::year(.),                  " ",
      two_digit_pad(lubridate::hour(.)),   ":",
      two_digit_pad(lubridate::minute(.)), ":",
      two_digit_pad(lubridate::second(.)), " EST"
    )
  } %>% {
    shiny::tagList(
      shiny::h3(paste0("Updated: ", .))
    )
  }
```

This page tracks the status of competition participants as they set up their
paper traders provided by [Interactive Brokers](https://www.interactivebrokers.com/en/home.php).

Check back here often - if the account ID logged for your tradername is not
correct, respond to the Duke Fintech Trading Competition email address or post
in the Slack channel ASAP.

```{r, echo = FALSE, include=FALSE}
completion_plot <- tibble::tibble(
  'status' = c('READY', 'INCOMPLETE'),
  'count'  = c(
    length(which(registry$account_id != 'account pending creation')),
    length(which(registry$account_id == 'account pending creation'))
  )
) %>%
  plotly::plot_ly(
    labels = ~status, 
    textposition = 'inside',
    textinfo = 'label+percent',
    insidetextfont = list(color = '#FFFFFF'),
    values = ~count, 
    type   = 'pie',
    marker = list(
      colors     = c('rgb(132,186,91)', 'rgb(128,133,133)'),
      line       = list(color = '#FFFFFF', width = 1)
    ),
    showlegend = FALSE
  ) %>% 
  plotly::layout(
    xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
    yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
    paper_bgcolor='rgba(0,0,0,0)',
    plot_bgcolor='rgba(0,0,0,0)'
  )

by_school_plot <- school_stats %>%
  dplyr::mutate(
    'bar_color' = completion %>%
      vapply(
        function(comp_pct){
          if(comp_pct < 0.5){
            return('rgb(139, 0, 0)')
          } else if(comp_pct < 1){
            return('rgba(55, 128, 191)')
          } else {
            return('rgb(132,186,91)') 
          }
        },
        character(1)
      )
  ) %>%
  plotly::plot_ly(
    x           = .$completion * 100,
    y           = .$school,
    type        = 'bar',
    color       = .$bar_color,
    height      = 900,
    orientation = 'h'
  ) %>% 
  plotly::layout(
    xaxis = list(
      color      = 'DarkGoldenRod', 
      ticksuffix = '%'
    ),
    yaxis = list(
      color     = 'GhostWhite', 
      autorange = 'reversed'
    ),
    showlegend    = FALSE,
    plot_bgcolor  ='rgba(0,0,0,0)',
    paper_bgcolor ='rgba(0,0,0,0)'
  )

shiny::tagList(
  shiny::fluidRow(
    shiny::column(
      width = 4, 
      shiny::fluidRow(
        shiny::tags$h3('Overall Completion', style = 'text-align: center')
      ),
      shiny::fluidRow(completion_plot)
    ),
    shiny::column(
      
      width = 8,
      shiny::fluidRow(
        shiny::tags$h3('Completion by School', style = 'text-align: center')
      ),
      shiny::div(by_school_plot, style='height: 400px;overflow-y: scroll;')
    )
  )
)

```


### Key

#### If your tradername doesn't appear here:
You've submitted your registration form but this website hasn't yet
refreshed and picked up your updated information.

#### 'account not yet active'
An IBKR account with your email does not yet appear in the response when the
Trading Competition App queries IBKR. This is either because you haven't
completed your Paper Trader Invitation form yet, or because your account is
still in the activation process, which can take one business day or longer.

#### An Account ID
Your account is set up and you're ready. The system has matched your tradername
to the given Account ID- you'll want to confirm that that's correct. Use the
Slack channel if there's an issue.


```{r, echo = FALSE}
DT::datatable(
  registry,
  extensions = 'Scroller', 
  rownames   = FALSE,
  options = list(
    columnDefs = list(list(className = 'dt-center', targets = '_all')),
    initComplete = DT::JS(
      "
      function(settings, json) {
          $(this.api().table().header()).css({
              'font-size' : '20px', 
              'color' : 'greenyellow'
          });
      }
      "
    ),
    buttons     = c('copy', 'csv', 'excel', 'pdf'),
    deferRender = TRUE,
    ordering    = FALSE,
    scrollY     = 500,
    scroller    = TRUE
  )
)
```
