---
title: "Registry"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Registry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include=FALSE, echo=FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
.dataTables_filter label {
  font-size: 18px;
  color: greenyellow;
}
```

### Key

#### If your tradername doesn't appear here:
You've submitted your registration form but this website hasn't yet
refreshed and picked up your updated information.

#### 'pending account creation'
You've been sent a welcome email and an IBKR paper trading account invitation.
Join the Slack channel, submit your IBKR form, and wait (about one business day)

#### An Account ID
Your account is set up and you're ready. The system has matched your tradername
to the given Account ID- you'll want to confirm that that's correct. Use the
Slack channel if there's an issue.


```{r, echo = FALSE}
DT::datatable(
  registry,
  extensions = 'Scroller', 
  rownames   = FALSE,
  options = list(
    columnDefs = list(list(className = 'dt-center', targets = '_all')),
    initComplete = DT::JS(
      "
      function(settings, json) {
          $(this.api().table().header()).css({
              'font-size' : '20px', 
              'color' : 'greenyellow'
          });
      }
      "
    ),
    deferRender = TRUE,
    ordering    = FALSE,
    scrollY     = 500,
    scroller    = TRUE
  )
)
```
