---
title: "Sharpe Ratio Calculation"
author: "Jake Vestal"
date: "3/15/2021"
---

```{css, echo=FALSE}
.dt-colnames {
  color: #fcba03;
}
```

```{r setup, include = FALSE}
library(magrittr)
student_data <- tibble::tibble(
  "EoD Portfolio Balance"  = c(
    999950, 999890, 1000100, 1000050, 1000250, 1000075, 1000301
  ),
  "Port. Return (%/trd day)" = c(
    NA, 
    log(
      `EoD Portfolio Balance`[-1] / 
        `EoD Portfolio Balance`[-length(`EoD Portfolio Balance`)]
    )
  ),
  "USDT 3 Mo CMT (%/yr)"      = rev(
    c(
      0.01, 0.03, 0.01, 0.01, 0.02, 0.02, 0.04
    )
  ) / 100,
  "USDT 3 Mo CMT (%/trd day)" = `USDT 3 Mo CMT (%/yr)`/252,
  "Excess Return (%/trd day)" = 
    `Port. Return (%/trd day)` - `USDT 3 Mo CMT (%/trd day)`
)

gmrr_excess_return <- student_data$`Excess Return (%/trd day)`[-1] %>%
  as.numeric() %>% {
    prod(1 + .)^(1/length(.)) - 1
  }

portfolio_vol      <- sd(student_data$`Excess Return (%/trd day)`[-1])

sharpe_ratio <- gmrr_excess_return / portfolio_vol
```

# Scoring for an example student
As discussed in the
[Scoring](https://gothic-hedge-society.github.io/fintech.trading.competition/)
section, student performance is graded by Sharpe Ratio. Here, we walk through an
example that explains how the Sharpe Ratio would be calculated for an example
contest participant.

### Example Student's Data
Let's say that today's date is 23 March 2021, and a student has been
participating in the competition for seven days. Her end-of-day (EoD) portfolio
balance, daily portfolio return, risk free rates, and daily excess return are as
given in the table below:

``` {r echo = FALSE, message = FALSE}
student_data %>%
  DT::datatable(
    filter = "none",
    options = list(
      columnDefs = list(
        list(className = 'dt-center', targets = 0:5),
        list(className = 'dt-colnames', targets = 0:5)
      ),
      dom        = "t",
      ordering   = FALSE
    ),
    rownames = rev(
      c(
        "2021-03-23", "2021-03-22", "2021-03-19", "2021-03-18", "2021-03-17", 
        "2021-03-16", "2021-03-15"
      )
    )
  ) %>%
  DT::formatCurrency("EoD Portfolio Balance") %>%
  DT::formatPercentage("USDT 3 Mo CMT (%/yr)",  2) %>% 
  DT::formatPercentage(
    c(
      "Port. Return (%/trd day)", "Excess Return (%/trd day)"
    ),
    4
  ) %>%
  DT::formatPercentage("USDT 3 Mo CMT (%/trd day)", 6)

```

The student's **daily portfolio returns** are the log returns of her daily
portfolio value. For example, on 18 March 2021, she started the day with
\$1,000,100.00 and ended with \$1,000,050.00 in total portfolio value. Therefore
her return for that day was:
```{r}
paste0(round(log(1000050.00 / 1000100.00) * 100, 5), "%")
```

Note that there's no way to calculate a return on the very first day because
there's nothing to compare it to.

The **risk free rate**, $r_{f}$ is assumed to be the 3 month CMT rate as
published by the US Department of the Treasury (USDT). A quick visit to the
[USDT's website
](https://www.treasury.gov/resource-center/data-chart-center/interest-rates/pages/TextView.aspx?data=yieldYear&year=2021)
confirms the rates presented in the table. The USDT presents CMT rates in an
annualized format. Because the student's daily returns are on a *per trading day
basis*, we convert the annualized CMTs to a trading day basis by dividing by 252
-- the number of trading days in one year.

The student's **excess return** on any given day is determined by how much her
portfolio return exceeded the risk free rate on that day; in other words, her
*excess return* is the difference between her portfolio's return and the risk
free rate.

The student's overall **geometric mean excess return** $R_{p}$ is calculated as:
```{r}
# Note that here, I'm rounding the returns to 4 digits, so the final answer will
# differ slightly than the one reported in the table (and used for official
# scoring) due to this rounding error.
student_excess_gmrr <- (
  (1 + -0.0061) * (1 + 0.0209) * (1 + -0.0050) * 
    (1 + 0.0200) * (1 + -0.0176) * (1 + 0.0226)
)^(1/6) - 1

print(paste0(round(student_excess_gmrr*100, digits = 4), "%"))

```

The students **volatility of returns** $\sigma^{2}_{r}$ is the standard deviation of her excess gmrr:
```{r}
student_vol <- sd(c(-0.0061, 0.0209, -0.0050, 0.0200, -0.0176, 0.0226))
print(paste0(round(student_vol*100, digits = 3), "%"))
```

Finally, we can calculate the Sharpe Ratio for this student.

\begin{align*}
{\tt Sharpe\ Ratio} = \frac{R_{p} - r_{f}}{\sigma^{2}} 
\end{align*}

#### Wherein:

\begin{align*}
R_{p} & {\sf: Portfolio\ Return} \\
r_{f} & {\sf: Risk\ free\ rate\ of\ return} \\
\sigma^{2}_{r} & {\sf: Volatility\ of\ return}
\end{align*}

## Her Sharpe is:
```{r}
student_Sharpe <- student_excess_gmrr / student_vol
print(student_Sharpe)
```
Note that we've already taken the "$-r_{f}$" into account when we used the
excess gmrr instead of the gmrr of the daily returns.
