---
title: "traderpage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{traderpage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

  
```{r, include = FALSE}
devtools::load_all(".")
# library(crosstalk)
# sd <- SharedData$new(
#   reports %>% 
#     tidyr::unnest(statement) %>%
#     dplyr::select(date, rank, dplyr::everything()) %>%
#     dplyr::rename(α = alpha, β = beta) %>%
#     dplyr::arrange(trader_name, dplyr::desc(date))
# )
# page_length <- reports$statement %>%
#   vapply(
#     function(x){nrow(x)},
#     numeric(1)
#   ) %>%
#   unique()
```

```{css, echo=FALSE}
th {
  background-color: #222 !important;
}
div.dataTables_filter label {
    color: goldenrod !important;
  }
```


Use this page to check on your registration! You can search for your trader_name 
using the search bar. 

Timestamp of last update: **`r Sys.time()`**

This page is updated every evening until the start of the competition. 

Please check that you're able to sign in to the account listed beside your 
trader_name. If you have more than one account, contact the admins on Discord 
and let us know which account you want to use. 

If your name does *not* appear on this list, check the timestamp of last update,
above. If you created your account near that time, then its possible that the 
system can't see it yet; just wait a day. If you created your account more than 
3 hours before the timestamp, then post in the Discord. 

```{r echo=FALSE}
has_accounts <- file.path(
  rprojroot::find_package_root_file(), 'inst', 'has_ibkr_accounts.csv'
) %>%
  readr::read_csv(show_col_types = FALSE)
DT::datatable(
  has_accounts,
  rownames = FALSE,
  extensions = 'FixedColumns',
  options = list(
    dom          = 'ft',
    scrollX      = TRUE,
    scrollY      = '350px',
    ordering     = FALSE,
    pageLength   = nrow(has_accounts),
    initComplete = DT::JS(
      "function(settings, json) {",
      "$(this.api().table().header()).css(",
      "{'color': 'greenyellow', 'background-color': '#222'});",
      "}"
    ),
    columnDefs = list(
      list(className = 'dt-center', targets=0:2)
    )
  )
) %>%
  DT::formatStyle(
    columns = c('accountId', 'trader_name', 'discord_username'), 
    color = 'lightgoldenrodyellow'
  )
# shiny::fluidRow(
#   filter_select(
#     id         = "trader", 
#     label      = "Select Trader", 
#     sharedData = sd, 
#     group      = ~trader_name,
#     multiple   = FALSE
#   ),
#   sd %>%
#     DT::datatable(
#       rownames = FALSE,
#       extensions = 'FixedColumns',
#       options = list(
#         dom          = 't',
#         scrollX      = TRUE,
#         scrollY      = '350px',
#         ordering     = FALSE,
#         fixedColumns = TRUE,
#         pageLength   = page_length,
#         initComplete = DT::JS(
#           "function(settings, json) {",
#           "$(this.api().table().header()).css(",
#           "{'color': 'greenyellow', 'background-color': '#222'});",
#           "}"
#         ),
#         columnDefs = list(
#           list(className = 'dt-center', targets=1:14),
#           list(visible=FALSE, targets=c(2,3,4,6,8,11,12))
#         )
#       )
#     ) %>%
#     DT::formatCurrency(c('NAV', 'sp500_close')) %>%
#     DT::formatPercentage(
#       c('daily_return', 'sp500_return', 'gmrr', 'vol', 'α', 'excess_rtn'), 
#       digits=4
#     ) %>%
#     DT::formatSignif(c('β', 'sharpe'), digits=4) %>%
#     DT::formatStyle('date', color = 'goldenrod', backgroundColor = '#222') %>%
#     DT::formatStyle(
#       c(
#         'rank', 'NAV', 'sp500_close', 'daily_return', 'sp500_return', 'gmrr',
#         'vol', 'α', 'β', 'excess_rtn', 'sharpe'
#       ),
#       color    = '#f0f0f0',
#       fontSize = '0.75em'
#     )
# )
```
