---
title: "Scoring: Example Calculation"
output: html_document
---

```{css, echo=FALSE}
.dt-colnames {
color: #fcba03;
}
```

```{r setup, include = FALSE}
library(magrittr)
student_data <- tibble::tibble(
  "EoD Portfolio Balance"  = c(
    999950, 999890, 1000100, 1000050, 1000250, 1000075, 1000301
  ),
  "Port. Return (%/trd day)" = c(
    NA, 
    log(
      `EoD Portfolio Balance`[-1] / 
        `EoD Portfolio Balance`[-length(`EoD Portfolio Balance`)]
    )
  ),
  "SP500 Index" = c(
    4404.39, 4436.01, 4387.55, 4387.55, 4399.77, 4369.71, 4370.36	
  ),
  "SP500 Return (%/trd day)" = c(
    NA, 
    log(
      `SP500 Index`[-1] / 
        `SP500 Index`[-length(`SP500 Index`)]
    )
  ),
  "Excess Return (%/trd day)" = 
    `Port. Return (%/trd day)` - `SP500 Return (%/trd day)`
)

gmrr_excess_return <- student_data$`Excess Return (%/trd day)`[-1] %>%
  as.numeric() %>% {
    prod(1 + .)^(1/length(.)) - 1
  }

portfolio_vol      <- sd(student_data$`Excess Return (%/trd day)`[-1])

sharpe_ratio <- gmrr_excess_return / portfolio_vol
```

# Scoring for an example student
As discussed in the
[Scoring](https://gothic-hedge-society.github.io/fintech.trading.competition/articles/Scoring.html)
section, student performance is graded by Sharpe Ratio. Here, we walk through an
example that explains how the Sharpe Ratio would be calculated for an example
contest participant.

### Matching up Calculations w/ Excel and Other Programs
As simple as it may seem, calculating logarithms can differ slightly (or
sometimes, significantly) depending on the precision of the program you use.
It's possible to get different answers for the same log calcs in Excel, R, and
Python, and the difference gets magnified when calculating GMRR.

Therefore, don't worry too much if you try to follow along this example and wind
up with numbers that differ slightly. For the purposes of fairness in the
competition, it only matters that we use the same program for everyone -- which,
in this case, is the *log*() function in R.

### Example Student's Data
Let's say that today's date is 24 August 2023, and a student has been
participating in the competition for seven days. Her end-of-day (EoD) portfolio
balance, daily portfolio return, risk free rates, and daily excess return are as
given in the table below:

``` {r echo = FALSE, message = FALSE}
student_data %>%
  DT::datatable(
    filter = "none",
    options = list(
      columnDefs = list(
        list(className = 'dt-center', targets = 0:5),
        list(className = 'dt-colnames', targets = 0:5)
      ),
      dom        = "t",
      ordering   = FALSE
    ),
    rownames = c(
      "2023-08-24", "2023-08-23", "2023-08-22", "2023-08-21", "2023-08-18", 
      "2023-08-17", "2023-08-16"
    )
  ) %>%
  DT::formatCurrency("EoD Portfolio Balance") %>%
  DT::formatPercentage("SP500 Return (%/trd day)",  4) %>% 
  DT::formatPercentage(
    c(
      "Port. Return (%/trd day)", "Excess Return (%/trd day)"
    ),
    4
  ) 

```

The student's **daily portfolio returns** are the log returns of her daily
portfolio value. For example, on 21 August 2023, she started the day with
\$1,000,250.00 and ended with \$1,000,050.00 in total portfolio value. Therefore
her return for that day was:
```{r}
# 'log()' here is the natural log, not base 10.
paste0(round(log(1000050.00 / 1000250.00) * 100, 5), "%")
```

Note that there's no way to calculate a return on the very first day because
there's nothing to compare it to.

The **benchmark** for this contest is taken to be the S&P 500 index as described
in the [Scoring](https://gothic-hedge-society.github.io/fintech.trading.competition/articles/Scoring.html) section.

The student's **excess return** on any given day is determined by how much her
portfolio return exceeded the risk free rate on that day; in other words, her
*excess return* is the difference between her portfolio's return and the risk
free rate.

The student's overall **geometric mean excess return** $R_{p}$ is calculated as:
```{r}
# Note that here, I'm rounding the returns to 4 digits, so the final answer will
# differ slightly than the one reported in the table (and used for official
# scoring) due to this rounding error.
student_excess_gmrr <- (
  (1 + -0.0061) * (1 + 0.0209) * (1 + -0.0050) * 
    (1 + 0.0200) * (1 + -0.0176) * (1 + 0.0226)
)^(1/6) - 1

print(paste0(round(student_excess_gmrr*100, digits = 4), "%"))

```

The trader's **volatility of returns** $\sigma^{2}_{r}$ is the standard 
deviation of her portfolio's returns:
```{r}
student_vol <- sd(c(-0.0061, 0.0209, -0.0050, 0.0200, -0.0176, 0.0226))
print(paste0(round(student_vol*100, digits = 3), "%"))
```

Finally, we can calculate the Sharpe Ratio for this student.

\begin{align*}
{\tt Sharpe\ Ratio} = \frac{R_{p,e}}{\sigma^{2}} 
\end{align*}

#### Wherein:

\begin{align*}
R_{p,e} & {\sf: Excess\ Portfolio\ Return} \\
\sigma^{2}_{r} & {\sf: Volatility\ of\ return}
\end{align*}

Note that we've already taken the "$-r_{f}$" into account when we used the
excess gmrr instead of the gmrr of the daily returns; in other words, with this
notation the term "$R_{p} - r_{f}$" (as written in the
[Scoring](https://gothic-hedge-society.github.io/fintech.trading.competition/)
section) equals $R_{p,e}$.

## Her Sharpe is:
```{r}
student_Sharpe <- student_excess_gmrr / student_vol
print(student_Sharpe)
```
